The corona of a fully convective star with a near-polar flare

### 2023-12-19 src/tex/ms.tex
[showyourwork] overleaf sync

We note that not using the full set of observations as the prior resulted in an unconstrained hot coronal component during the flare. This can be interpreted as due to a lack of X-ray flux above $5\,$keV. Hot flares with temperatures of $>50\,$MK have been measured on DS~Tuc~A~\citep{pillitteri2011xray}. On the Sun, the highest flare associated coronal temperatures are around $35\,$MK~\citep{kay2003soft}.

@@

\begin{equation}
    f(E) \mathrm{d} E = \beta \cdot E^{-\alpha} \mathrm{d} E.
\end{equation}
following the procedure in~\citep{ilin2021flares}, implemented as \texttt{FFD.fit\_powerlaw} using the \textit{mcmc} argument in \texttt{AltaiPony}~\citep{ilin2021altaipony}, which is using the posterior distribution derived in \citet{wheatland2004bayesian}, and sampling the posterior distribution with the \texttt{emcee} package~\citep{foreman-mackey2013emcee}.

The FFD power law fit converged after 13,500 steps on a slope $\alpha =$\ffdalpha\unskip. The frequency $R_{31.5}$ of flares per day above $\log_{10} E_{\rm flare} = 31.5\,\mathrm{erg}$ is about $\log_{10}R_{31.5}=$\ffdr\unskip. The slope is typical of other flaring stars, regardless of spectral type and rotation period~(see, e.g., Fig.~13 in \citealt{ilin2021flares}). $R_{31.5}$ is typical of flaring M dwarfs, in particular typical of late M dwarfs in the saturated activity regime, where $R_{31.5}$ becomes independent of rotation period~\citep{medina2020flare,murray2022study}.

>>>>

We note that not using the full set of observations as the prior resulted in an unconstrained hot coronal component during the flare. This can be interpreted as due to a lack of X-ray flux above $5\,$keV. %Hot flares with temperatures of $>50\,$MK have been measured on DS~Tuc~A~\citep{pillitteri2011xray}. On the Sun, the highest flare associated coronal temperatures are around $35\,$MK~\citep{kay2003soft}.

@@

\begin{equation}
    f(E) \mathrm{d} E = \beta \cdot E^{-\alpha} \mathrm{d} E.
\end{equation}
following the procedure in~\citet{ilin2021flares}, implemented as \texttt{FFD.fit\_powerlaw} using the \textit{mcmc} argument in \texttt{AltaiPony}~\citep{ilin2021altaipony}, which is using the posterior distribution derived in \citet{wheatland2004bayesian}, and sampling the posterior distribution with the \texttt{emcee} package~\citep{foreman-mackey2013emcee}.

The FFD power law fit converged after 13,500 steps on a slope $\alpha =$\ffdalpha\unskip. The frequency $R_{31.5}$\textcolor{red}{, that is the frequency} of flares per day above $\log_{10} E_{\rm flare}\,[\mathrm{erg}] = 31.5$ is $\log_{10}R_{31.5}=$\ffdr\unskip. The slope is typical of other flaring stars, regardless of spectral type and rotation period~(see, e.g., Fig.~13 \textcolor{red}{of} \citealt{ilin2021flares}). $R_{31.5}$ is typical of flaring M dwarfs, in particular typical of late M dwarfs in the saturated activity regime, where $R_{31.5}$ becomes independent of rotation period~\citep{medina2020flare,murray2022study}.
